### 2014-06-25 reports/report.Rmd
Refine reports
report2

**Data contributor:** `r .dat$contact$name`.

**Email:** `r .dat$contact$email`.

**Address:** `r .dat$contact$address`.

## Citation
Information about the primary reference for the data you provided.

**Reference:** `r .dat$references$citation`

**DOI:** `r  bibGetElement(.dat$bib, element = "doi")`

**Abstract:** `r  bibGetElement(.dat$bib, element = "abstract")`

@@

Data for `r length(.dat$data$dataset)` individuals from `r length(unique(.dat$data$location))` locations covering `r length(unique(.dat$data$species))` species.

The dataset includes `r length(unique(.dat$data$species))` species belonging to `r length(unique(.dat$data$family))` family(ies), presenting `r length(unique(.dat$data$pft))` functional type(s), growing in `r length(unique(.dat$data$growingCondition))` condition(s) within `r length(unique(.dat$data$vegetation))` major type(s) of habitat:

### Number of records for each variable

```{r echo=FALSE, comment=''}
counts  <-  apply(!is.na(.dat$data), MARGIN=2, FUN = sum)
counts  <-  counts[counts>0]  #only include no zeros
counts  <-  counts[names(counts)%in%.dat$dictionary$Variable[.dat$dictionary$Group=="tree"]]
cbind(counts)
```

## Study details

### Location

**Location data**
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
options(width =160)
locLevelInfo(.dat$data)
```

**Global map**

```{r echo=FALSE, fig.width=8, fig.height=6, message=FALSE, warning=FALSE}
prepdata  <-  prepMapInfo(alldata$data, .study)
drawWorldPlot (prepdata)
```

**Country map**

```{r echo=FALSE, fig.width=8, fig.height=6, message=FALSE, warning=FALSE}
repMissingInfo(prepdata)
drawCountryPlot(prepdata)
```

**Stand description**
Information about the growing condition of plants in your study, i.e. their local environment.

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='', results="asis"}
kable(standLevelInfo(.dat$data))
```

### Species data

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='',results="asis"}
kable(spLevelInfo(.dat$data))
```

### Methods
```{r echo=FALSE, message=FALSE, warning=FALSE, comment='', results="asis"}
metaTable  <-  getMeta(.study)
writeLines(paste0(metaTable[,1], ": ", metaTable[,2], "\n"))
```

@@

This is how the study `r .study` (each colour represents a species) fits in the entire dataset (grey).

```{r fig.height=8, fig.width=8, echo=FALSE, warning=FALSE, message=FALSE}
makePlotPanel(alldata, .dat)
```

>>>>

**Data contributor:** `r .dat$contacts$name`

**Email:** `r paste0(.dat$contacts$email[.dat$contacts$email!=""], collapse = ", ")`

**Address:**

`r paste0("- ", .dat$contacts$address, collapse = "\n")`

## Data source

**Citation:** `r .dat$references$citation`

**DOI:** `r  paste0('[', bibGetElement(.dat$bibtex, element = "doi"), '](http://doi.org/', bibGetElement(.dat$bibtex, element = "doi"),')')`

**Abstract:** `r  bibGetElement(.dat$bibtex, element = "abstract")`

@@

The dataset includes records for `r length(.dat$data$studyName)` individuals from `r length(unique(.dat$data$species))` species belonging to `r length(unique(.dat$data$family))` family(ies), presenting `r length(unique(.dat$data$pft))` functional type(s), growing in `r length(unique(.dat$data$growingCondition))` condition(s) within `r length(unique(.dat$data$vegetation))` major type(s) of habitat, with data included for the following variables:

```{r results='asis', echo=FALSE, warning=FALSE}
options(digits=9)
kable(
	summaryTable(.dat$data, var.def= read.csv("../config/variableDefinitions.csv", stringsAsFactors=FALSE)),
	 "markdown", align="l", padding=10)
```

## Locations sampled

Data were sampled at the following locations:

```{r echo=FALSE, fig.width=12, fig.height=10, message=FALSE, warning=FALSE}
prepdata  <-  prepMapInfo(alldata$data, .study)
drawWorldPlot (prepdata)
```

And locally within the country:

```{r echo=FALSE, fig.width=12, fig.height=10, message=FALSE, warning=FALSE}
repMissingInfo(prepdata)
drawCountryPlot(prepdata)
```

The sites sampled are:

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='',results='asis'}
kable(locLevelInfo(.dat$data),"markdown", align="l", padding=2)
```

The growing conditions of sampled plants was:

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='', results="asis"}
kable(standLevelInfo(.dat$data),"markdown", align="l", padding=2)
```

## Species sampled

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='',results="asis"}
kable(spLevelInfo(.dat$data), "markdown", align="l", padding=2)
```

## Methods used

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='', results="asis"}
metaTable  <-  getMeta(.study)
writeLines(paste0("**",metaTable[,1],"**", ": ", metaTable[,2], "\n"))
```

@@

This is how the study `r .study` fits in the entire dataset (grey). each colour represents a species. A legend of species names with colours is included at the end for reports with 1 < n < 20 species.

```{r fig.height=12, fig.width=12, echo=FALSE, warning=FALSE, message=FALSE}
makePlotPanel(alldata, .dat)
```
